Capturing Policies for BYOD

### 2017-03-01 paper.tex
the rest of the tweaks requested from the reviewers

\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage[backend=bibtex,firstinits=true]{biblatex}
\addbibresource{paper.bib}
\makeatletter
\def\blx@maxline{77}
\makeatother

@@

\title{Capturing Policies for BYOD}
\author{Joseph Hallett and David Aspinall}
\institute{School of Informatics, University of Edinburgh}
\begin{document}
\maketitle
\begin{abstract}
  % 4 Sentences
  BYOD policies are informally specified using natural language.
  We show how the \AppPAL~language can help reduce ambiguity in 5 BYOD policies and link the specification of a BYOD policy to its implementation.
  Using a formalisation of the 5 policies written in \AppPAL, we make comparisons between them, and explore the delegation relationships within them.
  We identify that whilst policy acknowledgement is a key part of all 5 policies, they are not managed by existing MDM tools.
\end{abstract}
\section{Introduction}
\label{sec:intro}
% Describe the problem
% State my contribution
% 1 page

@@

Our approach taken with \AppPAL~is similar to work on safety cases.
A safety case is an argument made to say a system is acceptably safe to be used in a given scenario.
Industrial safety cases are often described in natural language, which can be ambiguous and unclear.
\ac{GSN}~\cite{kelly_goal_2004} is one approach to make the safety cases explicit.
It is a graphical formal notation that lets engineers argue that a system is safe by linking safety goals to the arguments made for a system's safety.
Similarly, work developing a formal language for specifying how medical staff should collaborate in a healthcare scenario~\cite{papapanagiotou_formal_2014} again helps clarify how roles are filled in a medical context on the basis of staff and different healthcare providers.

>>>>

\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage[backend=bibtex,firstinits=true,sorting=none]{biblatex}
\addbibresource{paper.bib}
\makeatletter
\def\blx@maxline{77}
\makeatother

@@

\title{Capturing Policies for BYOD}
\author{Joseph Hallett\thanks{Work supported by EPSRC App Guarden grant (EP/K032666/1); and the Alan Turing Institute.} and David Aspinall}
\institute{School of Informatics, University of Edinburgh}
\begin{document}
\maketitle
\begin{abstract}
  % 4 Sentences
  BYOD policies are informally specified using natural language.
  We show how the \AppPAL~language can help reduce ambiguity in 5 BYOD policies and link the specification of a BYOD policy to its implementation.
  Using a formalisation of the 5 policies written in \AppPAL, we make comparisons between them, and explore the delegation relationships within them.
  We identify that whilst policy acknowledgement is a key part of all 5 policies, they are not managed by existing MDM tools.
\end{abstract}
\section{Introduction}
\label{sec:intro}
% Describe the problem
% State my contribution
% 1 page

@@

Our approach taken with \AppPAL~is similar to work on safety cases.
A safety case is an argument made to say a system is acceptably safe to be used in a given scenario.
Industrial safety cases are often described in natural language, which can be ambiguous and unclear.
\ac{GSN}~\cite{tim_kelly_goal_2004} is one approach to make the safety cases explicit.
It is a graphical formal notation that lets engineers argue that a system is safe by linking safety goals to the arguments made for a system's safety.
Similarly, work developing a formal language for specifying how medical staff should collaborate in a healthcare scenario~\cite{papapanagiotou_formal_2014} again helps clarify how roles are filled in a medical context on the basis of staff and different healthcare providers.
